Author Guidelines for DAGM-OAGM Submission

### 2013-09-19 exact_learning/paper.tex
typographic fine-tuning :)

\chapter{Efficient Exact Learning of Loopy CRFs}\label{ch:exact_learning}

@@

In this chapter, we investigate the necessity and consequences of these
approximations in the one-slack cutting-plane learning algorithm in the context of semantic
image segmentation. We show that despite inference being deemed intractable in
loopy superpixel models, we are able to learn a pairwise conditional random
field model using a structured support vector machine exactly for this task.
We evaluate our approach on the popular MSRC-21 and Pascal VOC datasets. % and nyu?

@@

%Currently the most widely used method is the one-slack cutting plane formulation
%introduced by \citet{joachims2009cutting}.
%This work also introduced the caching of constraints,
%which serves as a basis for our work. We improve upon their caching scheme, and in
%particular consider how it interacts with approximate inference algorithms.

Recently, there has been an increase in research in learning structured
prediction models where standard exact inference techniques are not applicable,
in particular in the computer vision community.
The influence of approximate inference on structural support vector machine
learning was first analyzed by  \citet{finley2008training}.
\citet{finley2008training} show convergence results for under-generating and
over-generating inference procedures, meaning methods that find suboptimal, but
feasible solutions, and optimal solutions from a larger (unfeasible) set,
respectively.
\citet{finley2008training} demonstrate that over-generating approaches---in
particular linear programming (LP)---perform best on the considered model.
They also show that learning parameters with the LP relaxation minimizes a
bound on the empirical risk when extending the target domain to the relaxed
solutions.
In contrast, we aim at optimizing the non-relaxed objective directly, minimizing
the original empirical risk. This is an important difference, as relaxed solutions
are usually not acceptable in practice.

@@

\begin{algorithm*}[t]
    \caption{1-Slack Cutting Plane Training of Structural SVMs \label{alg_one_slack_again}}
    \begin{algorithmic}[1]
        \Require training samples $\{ (x\hoch{i}, y\hoch{i}), \dots, (x\hoch{i}, y\hoch{i})\}$, regularization parameter $C$, stopping tolerance $\epsilon$.
        \Ensure parameters $\theta$, slack $\xi$
        \State $\W \leftarrow \emptyset$
        \Repeat
            \State \label{line_restricted}
            \vspace{-5mm}
            \begin{align*}
                (\theta, \xi) \leftarrow \displaystyle &\argmin_{\theta, \xi} \frac{||\theta||}{2}^2 + C \xi\\
            &\text{s.t. }\forall \hat{\mathbf{y}}=(\hat{y}\hoch{1}, \dots, \hat{y}\hoch{k}) \in \W:\\
            &\theta^T \sum_{i=1}^k [\psi(x\hoch{i}, y\hoch{i}) - \psi(x\hoch{i}, \hat{y}\hoch{i})] \geq \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}\hoch{i}) - \xi
            \end{align*}
            \For {i=1, \dots, k}
                \State
                $\hat{y}\hoch{i} \leftarrow I(x\hoch{i}, y\hoch{i}, \theta) := \displaystyle \argmax_{\hat{y}\in\mathcal{Y}} \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}) - \theta^T \sum_{i=1}^k [\psi(x\hoch{i}, y\hoch{i}) - \psi(x\hoch{i}, \hat{y})]$ \label{get_cutting_plane_again}
            \EndFor
            \State $\W \leftarrow \W \cup \{ (\hat{y}\hoch{i}, \dots, \hat{y}\hoch{i}) \} $
            \State $ \displaystyle \xi' \leftarrow  \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}\hoch{i}) - \theta^T \sum_{i=1}^k [\psi(x\hoch{i}, y\hoch{i}) - \psi(x\hoch{i}, \hat{y}\hoch{i})] $
        \Until $\xi' - \xi < \epsilon$ \label{convergence_check}
    \end{algorithmic}
\end{algorithm*}

\section{Learning SSVMs with Approximate Inference}
In this chapter, we use the 1-slack cutting plane algorithm, as we found this
algorithm to be most suitable for out approach. For reference, the algorithm described in
\Secref{one_slack}, Algorithm~\ref{alg_one_slack_again} is reproduced as
Algorithm~\ref{alg_one_slack_again}. The inference algorithm $I$ is called in
line~\ref{get_cutting_plane_again}. We investigate algorithms $I$ (often called
separation
oracles in the context) that do not yield the exact maximum here.
There are two groups of inference procedures, as identified in
\citet{finley2008training}: under-generating and over-generating approaches.
An under-generating approach satisfies $I(x^i, y^i, \theta) \in
\mathcal{Y}$, but does not guarantee maximality in line~\ref{get_cutting_plane_again}
of Algorithm~\ref{alg_one_slack_again}. An over-generating approach on the other
hand, does solve the loss-augmented prediction in line~\ref{get_cutting_plane_again}
exactly, but for a larger set $\hat{\mathcal{Y}} \supset \mathcal{Y}$, meaning
that possibly $I(x^i, y^i, \theta) \notin \mathcal{Y}$.
%We elaborate on
%the properties of under-generating and over-generating inference procedures in
%Section~\ref{bounds}. %TODO Filler sentence? wat?

\subsection{Bounding the Objective}\seclabel{bounds}
Even using approximate inference procedures, several statements
about the original exact objective (\Eqref{mainequation}) can be
obtained.

Let $o_{\W}(\theta)$ denote objective \Eqref{oneslack} with
given parameters $\theta$ restricted to a working set $\W$, as computed in
line~\ref{line_restricted} of Algorithm~\ref{alg_one_slack_again} and  let
\[
    o^I(\theta) = C\xi' + \frac{||\theta||}{2}^2
\]
when using inference algorithm $I$, that is $o^I(\theta)$ is the approximation of the primal
objective given by $I$. To simplify exposure, we drop the dependency on $\theta$.

Depending on the properties of the inference procedure $I$ used, it is easy to see:
\begin{enumerate}
    \item If all constraints $\hat{y}$ in  $\W$ are feasible, that is generated
        by an under-generating or exact inference mechanism, then $o_{\W}$ is
        an lower bound on the true optimum $o(\theta^*)$.

    \item If $I$ is an over-generating or exact algorithm, $o^I$ is an upper
        bound on $o(\theta^*)$.
\end{enumerate}

@@

\subsection{Combining Inference Procedures}\seclabel{combining}
The cutting plane method described in \Secref{one_slack} relies only
on some separation oracle $I$ that produces violated constraints when
performing loss-augmented prediction.

Using any under-generating oracle $I$, learning can proceed as long as a
constraint is found that is violated by more than the stopping tolerance
$\epsilon$.  Which constraint is used next has an impact on the speed of
convergence, but not on correctness. Therefore, as long as an under-generating
method does generate constraints, optimization makes progress on the objective.

@@

%objective given by $I$. To simplify exposure, we drop the dependency on $\theta$.
In the following, we use the notation of \Secref{bounds} and indicate
the choices of oracle $I$ with $Q$ for a chosen inference algorithm and $C$ for
using cached constraints.

@@

\begin{table}
    \begin{center}
    \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcc}
    \toprule
                    & Move-making & Exact \\
    \cmidrule{1-3}
    Dual Objective $o_\W$ & 65.10 & 67.66  \\
    Estimated Objective $o^I$ &  67.62& 67.66\\
    True Primal Objective $o^E$& 69.92& 67.66\\
    \bottomrule
    \end{tabularx}
    \end{center}
    \caption{Objective function values on the MSRC-21 Dataset}
    \tablabel{msrc_objective}
\end{table}

@@

The objective function values using only the under-generating move-making and
the exact inference are detailed in \Tabref{msrc_objective} and \Tabref{pascal_objective}.
We see that a significant gap between the cutting plane objective and the primal objective
remains when using only under-generating inference.
Additionally, the estimated primal objective $o^I$ using under-generating inference is
too optimistic, as can be expected. This underlines the fact that
under-generating approaches can not be used to upper-bound the primal
objective or compute meaningful duality gaps.

\begin{table}
    \begin{center}
    \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcc}
    \toprule
                    & Move-making & Exact \\
    \cmidrule{1-3}
    Dual Objective $o_\W$ &92.06& 92.24\\
    Estimated Objective $o^I$ & 92.07 &92.24\\
    True Primal Objective $o^E$&92.35& 92.24  \\
    \bottomrule
    \end{tabularx}
    \end{center}
    \caption{Objective function values on the Pascal Dataset.}
    \tablabel{pascal_objective}
\end{table}

\subsection{Implementation Details}
We implemented the described procedure in \pystruct.

We used the SLIC implementation provided by \citet{achanta2012slic} to extract superpixels and
the SIFT implementation in the \texttt{vlfeat} package~\citep{vedaldi08vlfeat}.
For clustering visual words, piecewise training of unary potentials and the
approximation to the $\chi^2$-kernel, we made use of the \texttt{scikit-learn}
machine learning package~\citep{pedregosa2011scikit}.
%TODO implementation details here?
The move-making algorithm using QPBO is implemented with the help of the QPBO-I
method provided by \citet{rother2007optimizing}.
We use the excellent implementation of AD$^3$ provided by the authors of
\citet{martins2011augmented}.

@@

\section{Summary}
In this chapter we demonstrated that it is possible to learn state-of-the-art
conditional random field models exactly using structural support vector
machines, despite the model containing many loops.  The key to efficient
learning is the combination of different inference mechanisms and a novel
caching scheme for the one-slack cutting plane method, in combination with
state-of-the-art inference methods.

We show that guaranteeing exact results is feasible in a practical setting, and
hope that this result provides a new perspective onto learning loopy models for
computer vision applications.
%
Even though exact learning does not necessarily lead to a large improvement in
accuracy, it frees the practitioner from worrying about optimization and
approximation issues, leaving more room for improving the model, instead of the
optimization.

We do not expect learning of pixel-level models, which typically have tens or
hundreds of thousands of variables, to be efficient using exact inference. However we
believe our results will carry over to other super-pixel based approaches.
Using other over-generating techniques, such as duality-based message passing
algorithms, it might be possible to obtain meaningful bounds on the true
objective, even in the pixel-level domain.

>>>>

\chapter{Learning of Loopy CRF Exactly}\label{ch:exact_learning}

@@

In this chapter, we investigate the necessity and consequences of these
approximations in the $1$-slack cutting-plane learning algorithm in the context of semantic
image segmentation. We show that despite inference being deemed intractable in
loopy superpixel models, we are able to learn a pairwise conditional random
field model using a structured support vector machine exactly for this task.
We evaluate our approach on the popular MSRC-21 and Pascal VOC datasets. % and nyu?

@@

%Currently the most widely used method is the $1$-slack cutting plane formulation
%introduced by \citet{joachims2009cutting}.
%This work also introduced the caching of constraints,
%which serves as a basis for our work. We improve upon their caching scheme, and in
%particular consider how it interacts with approximate inference algorithms.

Recently, there has been an increase in research in learning structured
prediction models where standard exact inference techniques are not applicable,
in particular in the computer vision community.
The influence of approximate inference on structural support vector machine
learning was first analyzed by  \citet{finley2008training}.
\citet{finley2008training} show convergence results for under-generating and
over-generating inference procedures, meaning methods that find suboptimal, but
feasible solutions, and optimal solutions from a larger (unfeasible) set,
respectively.
\citet{finley2008training} demonstrate that over-generating approaches---in
particular linear programming (LP)---perform best on the considered model.
They also show that learning parameters with the LP relaxation minimizes a
bound on the empirical risk when extending the target domain to the relaxed
solutions.
We argue that extending the target domain in this way is unnatural for many applications,
and aim at optimizing the non-relaxed objective directly, minimizing
the original empirical risk. This is an important difference, as relaxed solutions
are usually not acceptable in practice.

@@

\begin{algorithm*}[t]
    \caption{1-Slack Cutting Plane Training of Structural SVMs \label{alg_one_slack_again}}
    \begin{algorithmic}[1]
        \Require training samples $\{ (x\hoch{i}, y\hoch{i}), \dots, (x\hoch{i}, y\hoch{i})\}$, regularization parameter $C$, stopping tolerance $\epsilon$, inference oracle $\hat{I}$.
        \Ensure parameters $\theta$, slack $\xi$
        \State $\W \leftarrow \emptyset$
        \Repeat
            \State \label{line_restricted}
            \vspace{-5mm}
            \begin{align*}
                (\theta, \xi) \leftarrow \displaystyle &\argmin_{\theta, \xi} \frac{||\theta||}{2}^2 + C \xi\\
            &\text{s.t. }\forall \hat{\mathbf{y}}=(\hat{y}\hoch{1}, \dots, \hat{y}\hoch{k}) \in \W:\\
            &\theta^T \sum_{i=1}^k [\psi(x\hoch{i}, y\hoch{i}) - \psi(x\hoch{i}, \hat{y}\hoch{i})] \geq \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}\hoch{i}) - \xi
            \end{align*}
            \For {i=1, \dots, k}
                \State
                $\hat{y}\hoch{i} \leftarrow \hat{I}(x\hoch{i}, y\hoch{i}, \theta) \approx \displaystyle \argmax_{\hat{y}\in\mathcal{Y}} \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}) - \theta^T \sum_{i=1}^k [\psi(x\hoch{i}, y\hoch{i}) - \psi(x\hoch{i}, \hat{y})]$ \label{get_cutting_plane_again}
            \EndFor
            \State $\W \leftarrow \W \cup \{ (\hat{y}\hoch{i}, \dots, \hat{y}\hoch{i}) \} $
            \State $ \displaystyle \xi' \leftarrow  \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}\hoch{i}) - \theta^T \sum_{i=1}^k [\psi(x\hoch{i}, y\hoch{i}) - \psi(x\hoch{i}, \hat{y}\hoch{i})] $
        \Until $\xi' - \xi < \epsilon$ \label{convergence_check}
    \end{algorithmic}
\end{algorithm*}

\section{Learning SSVMs with Approximate Inference}
In this chapter, we use the $1$-slack cutting plane algorithm, as we found this
algorithm to be most suitable for out approach. Recall the optimization problem
that is solved by the $1$-slack cutting plane algorithm:
\begin{align}\eqlabel{oneslack_again}
    \min_{\theta, \xi}\ &\frac{1}{2} ||\theta||^2 + C \xi\\
    \text{s.t. }&\forall \hat{\mathbf{y}}=(\hat{y}^1, \dots, \hat{y}^n) \in \mathcal{Y}^n:\\
        &\theta^T \sum_{i=1}^n [\Phi(x^i, y^i) - \Phi(x^i,
            \hat{y}^i)] \geq \sum_{i=1}^n \Delta(y^i, \hat{y}^i)
            - \xi
\end{align}
For reference, the algorithm described in
\Secref{one_slack}, Algorithm~\ref{alg_one_slack} is reproduced as
Algorithm~\ref{alg_one_slack_again}, with the additional input of an inference algorithm $\hat{I}$, which is called in
line~\ref{get_cutting_plane_again}. We investigate algorithms $\hat{I}$ (often called
separation
oracles in the context) that do not yield the exact maximum here.
There are two groups of inference procedures, as identified in
\citet{finley2008training}: under-generating and over-generating approaches.
An under-generating approach satisfies $\hat{I}(x^i, y^i, \theta) \in
\mathcal{Y}$, but does not guarantee maximality in line~\ref{get_cutting_plane_again}
of Algorithm~\ref{alg_one_slack_again}. An over-generating approach on the other
hand, does solve the loss-augmented prediction in line~\ref{get_cutting_plane_again}
exactly, but for a larger set $\hat{\mathcal{Y}} \supset \mathcal{Y}$, meaning
that possibly $\hat{I}(x^i, y^i, \theta) \notin \mathcal{Y}$.
%We elaborate on
%the properties of under-generating and over-generating inference procedures in
%Section~\ref{bounds}. %TODO Filler sentence? wat?

\subsection{Bounding the Objective}\seclabel{bounds}
Even using approximate inference procedures, several statements
about the original exact objective (\Eqref{oneslack_again}) can be
obtained.

Let $o_{\W}(\theta)$ denote objective \Eqref{oneslack_again} with
given parameters $\theta$ restricted to a working set $\W$, as computed in
line~\ref{line_restricted} of Algorithm~\ref{alg_one_slack_again} and  let
\[
    o^{\hat{I}}(\theta) = C\xi' + \frac{||\theta||}{2}^2
\]
when using inference algorithm $\hat{I}$, that is $o^{\hat{I}}(\theta)$ is the approximation of the primal
objective given by $\hat{I}$. To simplify exposure, we drop the dependency on $\theta$.

Depending on the properties of the inference procedure $\hat{I}$ used, it is easy to see:
\begin{enumerate}
    \item If all constraints $\hat{y}$ in  $\W$ are feasible, that is generated
        by an under-generating or exact inference mechanism, then $o_{\W}$ is
        an lower bound on the true optimum $o(\theta^*)$.

    \item If $\hat{I}$ is an over-generating or exact algorithm, $o^{\hat{I}}$ is an upper
        bound on $o(\theta^*)$.
\end{enumerate}

@@

\subsection{Combining Inference Procedures}\seclabel{combining}
The cutting plane method described in \Secref{one_slack} relies only
on some separation oracle $\hat{I}$ that produces violated constraints when
performing loss-augmented prediction.

Using any under-generating oracle $\hat{I}$, learning can proceed as long as a
constraint is found that is violated by more than the stopping tolerance
$\epsilon$.  Which constraint is used next has an impact on the speed of
convergence, but not on correctness. Therefore, as long as an under-generating
method does generate constraints, optimization makes progress on the objective.

@@

%objective given by $I$. To simplify exposure, we drop the dependency on $\theta$.
In the following, we use the notation of \Secref{bounds} and indicate
the choices of oracle $\hat{I}$ with $Q$ for a chosen inference algorithm and $C$ for
using cached constraints.

@@

\begin{table}
    \begin{center}
    \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcc}
    \toprule
                    & Move-making & Exact \\
    \cmidrule{1-3}
    Dual Objective $o_\W$ & 65.10 & 67.66  \\
    Estimated Objective $o^{\hat{I}}$ &  67.62& 67.66\\
    True Primal Objective $o^E$& 69.92& 67.66\\
    \bottomrule
    \end{tabularx}
    \end{center}
    \caption{Objective function values on the MSRC-21 Dataset}
    \tablabel{msrc_objective}
\end{table}

@@

The objective function values using only the under-generating move-making and
the exact inference are detailed in \Tabref{msrc_objective} and \Tabref{pascal_objective}.
We see that a significant gap between the cutting plane objective and the primal objective
remains when using only under-generating inference.
Additionally, the estimated primal objective $o^{\hat{I}}$ using under-generating inference is
too optimistic, as can be expected. This underlines the fact that
under-generating approaches can not be used to upper-bound the primal
objective or compute meaningful duality gaps.

\begin{table}
    \begin{center}
    \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcc}
    \toprule
                    & Move-making & Exact \\
    \cmidrule{1-3}
    Dual Objective $o_\W$ &92.06& 92.24\\
    Estimated Objective $o^{\hat{I}}$ & 92.07 &92.24\\
    True Primal Objective $o^E$&92.35& 92.24  \\
    \bottomrule
    \end{tabularx}
    \end{center}
    \caption{Objective function values on the Pascal Dataset.}
    \tablabel{pascal_objective}
\end{table}

\subsection{Implementation Details}
We implemented the described procedure in \pystruct.
We used the SLIC implementation provided by \citet{achanta2012slic} to extract superpixels and
the SIFT implementation in the \texttt{vlfeat} package~\citep{vedaldi08vlfeat}.
For clustering visual words, piecewise training of unary potentials and the
approximation to the $\chi^2$-kernel, we made use of the \texttt{scikit-learn}
machine learning package~\citep{pedregosa2011scikit}.
%TODO implementation details here?
The move-making algorithm using QPBO is implemented with the help of the QPBO-I
method provided by \citet{rother2007optimizing}.
We use the excellent implementation of AD$^3$ provided by the authors of
\citet{martins2011augmented}.

@@

\section{Summary}
In this chapter we demonstrated that it is possible to learn state-of-the-art
conditional random field models exactly using structural support vector
machines, despite the model containing many loops.  The key to efficient
learning is the combination of different inference mechanisms and a novel
caching scheme for the $1$-slack cutting plane method, in combination with
state-of-the-art inference methods.

We show that guaranteeing exact results is feasible in a practical setting, and
hope that this result provides a new perspective onto learning loopy models for
computer vision applications.
%
Even though exact learning does not necessarily lead to a large improvement in
accuracy, it frees the practitioner from worrying about optimization and
approximation issues, leaving more room for improving the model, instead of the
optimization.
\enlargethispage{10mm}
We do not expect learning of pixel-level models, which typically have tens or
hundreds of thousands of variables, to be efficient using exact inference. However we
believe our results will carry over to other super-pixel based approaches.
Using other over-generating techniques, such as duality-based message passing
algorithms, it might be possible to obtain meaningful bounds on the true
objective, even in the pixel-level domain.

### 2013-09-19 intro.tex
typographic fine-tuning :)

We choose this task in particular for several reasons:
\begin{itemize}
    \item Pixel-level annotation provides highly detailed information about the scene.
    \item Joint estimation of multiple classes allows for the use of context.
    \item In contrast to category-agnostic segmentation approaches, object class segmentation
        has an unambiguous true labeling.
    \item A variety of manually annotated datasets is publicly available.
\end{itemize}
%
Applications of semantic segmentation and scene understanding include automatic
image interpretation for retrieval, autonomous driving and mobile robotics.
While these are already important applications, we expect that with the
abundance of camera data, and the proliferation of mobile computing, even
more applications will emerge soon.

@@

The main part of this thesis investigates the use of structured learning
algorithms to the task of semantic image segmentation. Both topics have receive
much attention in the computer vision and machine learning communities lately.
Unfortunately, learning structured prediction in computer vision applications
is still little understood.
We focus on the use of conditional random fields~(CRFs), which have shown great
promise for computer vision applications. Using the paradigm of structural
support vector machines, it is possible to learn conditional random fields to
directly minimize a loss of interest. In particular, conditional random fields
allow to combine different cues, possibly produced by other approaches, in a
principled manner. One of the main difficulties with CRF approaches to computer
vision problems is, that context in images is usually represented as a
neighborhood graph.  These graphs, by nature, contain many cycles, making
inference intractable in general. Consequently, learning algorithms have to
rely on approximate inference, with often unknown consequences to learning.

>>>>

We choose this task in particular for several reasons:
\begin{itemize*}
    \item Pixel-level annotation provides highly detailed information about the scene.
    \item Joint estimation of multiple classes allows for the use of context.
    \item In contrast to category-agnostic segmentation approaches, object class segmentation
        has an unambiguous true labeling.
    \item A variety of manually annotated datasets is publicly available.
\end{itemize*}
%
Applications of semantic segmentation and scene understanding include automatic
image interpretation for retrieval, autonomous driving and mobile robotics.
While these are already important applications, we expect that with the
abundance of camera data, and the proliferation of mobile computing, even
more applications will emerge soon.

@@

The main part of this thesis investigates the use of structured learning~\citep{taskar2003max, tsochantaridis2006large}
algorithms to the task of semantic image segmentation. Both topics have receive
much attention in the computer vision and machine learning communities
lately~\citep{ladicky2009associative, krahenbuhl2012efficient,
branson2013efficient, blake2011markov}.
Unfortunately, learning structured prediction in computer vision applications
is still little understood.
We focus on the use of conditional random fields~(CRFs), which have shown great
promise for computer vision applications. Using the paradigm of structural
support vector machines, it is possible to learn conditional random fields to
directly minimize a loss of interest. In particular, conditional random fields
allow to combine different cues, possibly produced by other approaches, in a
principled manner. One of the main difficulties with CRF approaches to computer
vision problems is, that context in images is usually represented as a
neighborhood graph.  These graphs, by nature, contain many cycles, making
inference intractable in general. Consequently, learning algorithms have to
rely on approximate inference, with often unknown consequences to learning.

### 2013-09-19 itm/paper.tex
typographic fine-tuning :)

A comparison of ITM, MeanNN and the baseline methods, $k$-Means and 
single link agglomerative clustering, in terms of their objective, 
optimization and complexity can be found in Table~\ref{nowotab}. 
We implemented the ITM clustering procedure as well as MeanNN in Python.  We
used the $k$-Means implementation available in the scikit-learn
library~\citep{pedregosa2011scikit}. The source
code is available online\footnote{\url{https://github.com/amueller/information-theoretic-mst}}.

>>>>

\enlargethispage{5mm}
A comparison of ITM, MeanNN and the baseline methods, $k$-Means and 
single link agglomerative clustering, in terms of their objective, 
optimization and complexity can be found in Table~\ref{nowotab}. 
We implemented the ITM clustering procedure as well as MeanNN in Python.  We
used the $k$-Means implementation available in the scikit-learn
library~\citep{pedregosa2011scikit}. The source
code is available online\footnote{\url{https://github.com/amueller/information-theoretic-mst}}.
